Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
subsection heading

\paragraph{Technical Factors:} We collected these factors from the 
MSR Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy the commit's
complexity, such as the size of the changes being performed.  The technical
factors used are listed below:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn: a count of the lines of code changed by this commit.
\item Files added: a count of the files added by this commit.
\item Files modified: a count of the files modified by this commit.
\item Tests added: a count of the tests added by this commit.
\item Tests deleted: a count of the tests deleted by this commit.
\item Source files: a count of the files in project at the time of the commit.
\item Source loc: a count of the lines of source code in the project at
	the time of the commit.
\item Travis status: status of the Travis build integration.
\end{itemize}

\paragraph{Social Factors:} To collect the social data, we created a web scraper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set provided by the MSR Challenge~\cite{msr17challenge} to locate the web page
of the commit, leveraging \textit{github.com}'s URL standard for projects and
commit hashes.
%  using the syntax
% below. 
% \newline \newline
% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
% \newline \newline

@@

\paragraph{Comparing two data sets:} We compiled all the gather data into 
two data sets: one with only the technical
factors and the build status, and another with both the technical and social
factors and the build status. We performed this split to analyze how well technical factors alone,
and then both technical and social
factors predict build integration status.

The data set used in this study~\cite{msr17challenge} is very diverse.
and consists of commits from multiple\todo{How many? Please be precise.} years ago. The social data we 
gather is recent, gathered in January 2017. In an effort to mitigate the threat of
using future result to predict previous events,
we removed the commits in the data set that were not performed within the last
three years of the data set's release (2014,2015,2016).  This is with the intuition that the social attributes are more likely to have similar values in the most recent years than if we were to consider the whole time span of the projects in the data set.

@@

\subsection{Success Classification}

\todo{a better subsection heading might be ``Classification with and without
  social factors.'', since all experiments look at success classification.}
Table~\ref{resultsTable} shows the results of running the two data sets through the
default Weka J48 decision tree algorithm.  Without downsampling, the 
decision tree shows an increase of 4.09\% correctly classified instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
had a classification accuracy of 64.10\%, which outperformed the baseline of
guessing all builds passed (50.00\%).
 After including the social data
in the data set, the classifier correctly predicted 76.09\% of the data set,
about a 12\% improvement from only the technical data.  These results show that
both technical and social data can be used to improve predictions of build 
integration success.

>>>>

\paragraph{Technical Factors} We collected these factors from the 
MSR Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy the commit's
complexity, such as the size of the changes being performed.  The technical
factors used are listed below:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn: a count of the lines of code changed by this commit.
\item Files added: a count of the files added by this commit.
\item Files modified: a count of the files modified by this commit.
\item Tests added: a count of the tests added by this commit.
\item Tests deleted: a count of the tests deleted by this commit.
\item Source files: a count of the files in project at the time of the commit.
\item Source loc: a count of the lines of source code in the project at
	the time of the commit.
\item Travis status: status of the Travis build integration.
\end{itemize}

\paragraph{Social Factors} To collect the social data, we created a web scraper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set provided by the MSR Challenge~\cite{msr17challenge} to locate the web page
of the commit, leveraging \textit{github.com}'s URL standard for projects and
commit hashes.
%  using the syntax
% below. 
% \newline \newline
% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
% \newline \newline

@@

\paragraph{Comparing two data sets} We compiled all the gather data into 
two data sets: one with only the technical
factors and the build status, and another with both the technical and social
factors and the build status. We performed this split to analyze how well technical factors alone,
and then both technical and social
factors predict build integration status.

The data set used in this study~\cite{msr17challenge} is very diverse,
and consists of commits that date as far back as 2011. The social data we 
gather is recent, gathered in January 2017. In an effort to mitigate the threat of
using future result to predict previous events,
we removed the commits in the data set that were not performed within the last
three years of the data set's release (2014,2015,2016).  This is with the intuition that the social attributes are more likely to have similar values in the most recent years than if we were to consider the whole time span of the projects in the data set.

@@

\subsection{Classification with and without social factors}

Table~\ref{resultsTable} shows the results of running the two data sets through the
default Weka J48 decision tree algorithm.  Without downsampling, the 
decision tree shows an increase of 4.09\% correctly classified instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
had a classification accuracy of 64.10\%, which outperformed the baseline of
guessing all builds passed (50.00\%).
 After including the social data
in the data set, the classifier correctly predicted 76.09\% of the data set,
about a 12\% improvement from only the technical data.  These results show that
both technical and social data can be used to improve predictions of build 
integration success.
